The benefits of reporting critical effect size values\footnote{The manuscript as been posted as a pre-print and has not yet undergone peer-review.}

### 2025-03-04 paper/paper.Rmd
adding equations with only sample size in the table

```{r eqsummary, echo=FALSE, tab.cap="Summary of the critical effect size equations, see text for details."}
library(kableExtra)

eqs <- data.frame(
  stringsAsFactors = FALSE,
             Model = c("One-sample t-test",
                       "Paired t-test","Paired t-test","Between-sample t-test",
                       "Correlation","Correlation","Meta-analysis/Regression"),
         Numerator = c("$b_c = t_c \\times \\mbox{SE}_b$","$b_c = t_c \\times \\mbox{SE}_b$",
                       "$b_{z_c} = t_c \\times \\mbox{SE}_b$",
                       "$b_c = t_c \\times \\mbox{SE}_b$",
                       "$r_c = \\frac{t_c}{\\sqrt{n - 2 + t^2_c}}$","$r_{z_c} = \\frac{z_c}{\\sqrt{n - 3}}$",
                       "$\\beta_c = t_c \\times \\mbox{SE}_{\\beta}$"),
       Denominator = c("$s$", NA, "$s_D$", "$s_p$", NA, NA, NA),
          Equation = c("$d_c = \\frac{t_c \\times \\mbox{SE}_b}{s}$",
                       "$d_c = \\frac{t_c \\times \\mbox{SE}_b}{s_p}$",
                       "$d_{z_c} = \\frac{t_c \\times \\mbox{SE}_b}{s_D}$",
                       "$d_c = \\frac{t_c \\times \\mbox{SE}_b}{s_p}$",
                       "$r_c = \\frac{t_c}{\\sqrt{n - 2 + t^2_c}}$","$r_{z_c} = \\frac{z_c}{\\sqrt{n - 3}}$",
                       "$\\beta_c = t_c \\times \\mbox{SE}_{\\beta}$")
)

>>>>

```{r eqsummary, echo=FALSE, tab.cap="Summary of the critical effect size equations, see text for details. When possible, we also included the equation to calculate the critical effect size without computing the standard error. For the paired t-test, this is feasible when using the standard deviation of differences. For the two-sample t-test, it is possible only under the assumption of homogeneity of variances."}
library(kableExtra)

eqs <- data.frame(
  stringsAsFactors = FALSE,
  Model = c("One-sample t-test",
            "Paired t-test","Paired t-test","Between-sample t-test",
            "Correlation test","Correlation","Meta-analysis/Regression"),
  Numerator = c("$b_c = t_c \\times \\mbox{SE}_b$","$b_c = t_c \\times \\mbox{SE}_b$",
                "$b_{z_c} = t_c \\times \\mbox{SE}_b$",
                "$b_c = t_c \\times \\mbox{SE}_b$",
                "$r_c = \\frac{t_c}{\\sqrt{n - 2 + t^2_c}}$","$r_{z_c} = \\frac{z_c}{\\sqrt{n - 3}}$",
                "$\\beta_c = t_c \\times \\mbox{SE}_{\\beta}$"),
  Denominator = c("$s$", NA, "$s_D$", "$s_p$", NA, NA, NA),
  Equation = c("$d_c = \\frac{t_c \\times \\mbox{SE}_b}{s} = t_c\\sqrt{\\frac{1}{n}}$",
               "$d_c = \\frac{t_c \\times \\mbox{SE}_b}{s_p}$",
               "$d_{z_c} = \\frac{t_c \\times \\mbox{SE}_b}{s_D} = t_c\\sqrt{\\frac{1}{n}}$",
               "$d_c = \\frac{t_c \\times \\mbox{SE}_b}{s_p} = t_c\\sqrt{\\frac{1}{n_1} + \\frac{1}{n_2}}$",
               "$r_c = \\frac{t_c}{\\sqrt{n - 2 + t^2_c}}$","$r_{z_c} = \\frac{z_c}{\\sqrt{n - 3}}$",
               "$\\beta_c = t_c \\times \\mbox{SE}_{\\beta}$")
)
